MIRSVM: Multi-Instance Support Vector Machine with Bag Representatives

### 2017-06-16 ArticleRevision/article/article.tex
Average Bag Size
> edited dataset table in paper to have average bag size
> wrote script to calculate dataset statistics and output them to a tex file

\begin{table}[t!]
\caption{Datasets used for the experiments in~\ref{subsec:results}}
\small
\label{tab:Dataset}
\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}ccccc}
\hline\noalign{\smallskip}
Dataset & Attributes & Positive Bags & Negative Bags & Total & Instances \\
\noalign{\smallskip}\hline\noalign{\smallskip}
Suramin 			& 20 	& 7 	& 4 	& 11 	& 2378 	\\
EastWest 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
WestEast 			& 24 	& 10 	& 10 	& 20 	& 213 	\\
Webmining			& 5863	& 17	& 58	& 75	& 2212	\\
Musk1 				& 166 	& 47 	& 45 	& 92 	& 476 	\\
Musk2 				& 166 	& 39 	& 63 	& 102 	& 6598 	\\
TRX 				& 8 	& 25 	& 193 	& 168 	& 26611 \\
Mutagenesis-Atoms 	& 10 	& 125 	& 63 	& 188 	& 1618 	\\
Mutagenesis-Bonds 	& 16 	& 125 	& 63 	& 188 	& 3995 	\\
Mutagenesis-Chains 	& 24 	& 125 	& 63 	& 188 	& 5349 	\\
Tiger 				& 230 	& 100 	& 100 	& 200 	& 1391 	\\
Elephant 			& 230 	& 100 	& 100 	& 200 	& 1220 	\\
Fox 				& 230 	& 100 	& 100 	& 200 	& 1320 	\\
Component			& 22	& 423	& 2707	& 3130	& 36894	\\
Function			& 202	& 443	& 4799	& 5242	& 55536	\\
\noalign{\smallskip}\hline
\end{tabularx}
\end{table}

>>>>

\begin{table}[t!]
\caption{Datasets used for the experiments in~\ref{subsec:results}}
\small
\label{tab:Dataset}
\begin{tabularx}{\textwidth}{l@{\extracolsep{\fill}}cccccc}
\hline\noalign{\smallskip}
Dataset & Attributes & Positive Bags & Negative Bags & Total & Instances & Average Bag Size\\
\noalign{\smallskip}\hline\noalign{\smallskip}
Suramin & 20 & 7 & 6 & 13 & 2898 &  222.92 \\ 
EastWest & 24 & 10 & 10 & 20 & 213 &  10.65  \\ 
WestEast & 24 & 10 & 10 & 20 & 213 &  10.65  \\ 
Musk1 & 166 & 47 & 45 & 92 & 476 &  5.17  \\ 
Musk2 & 166 & 39 & 62 & 101 & 6728 &  66.61  \\ 
Webmining & 5863 & 21 & 92 & 113 & 3423 &  30.29  \\ 
Mutagenesis-atoms & 10 & 125 & 63 & 188 & 1618 &  8.61  \\ 
Mutagenesis-bonds & 16 & 125 & 63 & 188 & 4081 &  21.71  \\ 
Mutagenesis-chains & 24 & 125 & 63 & 188 & 5424 &  28.85  \\ 
TRX & 8 & 25 & 168 & 193 & 26611 &  137.88 \\ 
Elephant & 230 & 100 & 100 & 200 & 1391 &  6.96 \\ 
Fox & 230 & 100 & 100 & 200 & 1320 &  6.60 \\ 
Tiger & 230 & 100 & 100 & 200 & 1188 &  5.94  \\ 
Component & 200 & 423 & 2707 & 3130 & 36894 &  11.79  \\ 
Function & 200 & 443 & 4799 & 5242 & 55536 &  10.59  \\ 
\noalign{\smallskip}\hline
\end{tabularx}
\end{table}
